---
output: rmarkdown::github_document
bibliography: README-refs.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`adaptest`

[![Travis-CI Build Status](https://travis-ci.org/wilsoncai1992/adaptest.svg?branch=master)](https://travis-ci.org/wilsoncai1992/adaptest?branch=master)
[![AppVeyor Build  Status](https://ci.appveyor.com/api/projects/status/github/wilsoncai1992/adaptest?branch=master&svg=true)](https://ci.appveyor.com/project/wilsoncai1992/adaptest/)
[![Coverage Status](https://img.shields.io/codecov/c/github/wilsoncai1992/adaptest/master.svg)](https://codecov.io/github/wilsoncai1992/adaptest?branch=master)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![GPL-2 License](http://img.shields.io/:license-gpl2-blue.svg)](http://www.gnu.org/licenses/gpl-2.0.html)
[![JOSS status](http://joss.theoj.org/papers/7618d7d14ac77f6f502df3f9eac5917d/status.svg)](http://joss.theoj.org/papers/7618d7d14ac77f6f502df3f9eac5917d)

> Data-adaptive statistics for multiple testing in high-dimensional problems

__Authors:__ Wilson Cai and [Nima Hejazi](http://nimahejazi.org)

---

## What's `adaptest`?

The `adaptest` R package is a tool for performing multiple testing on effect
sizes under high-dimensional settings, using the approach of data-adaptive
statistical target parameters and inference. For technical details on the
data-adaptive multiple testing procedure, consult @cai2018data. For an
introduction to statistical inference procedures using data-adaptive target
parameters, the interested reader is directed to @hubbard2016statistical.

---

## Installation

<!--
For standard use, install from [Bioconductor](https://bioconductor.org):
```{r bioc-installation, eval = FALSE}
source("https://bioconductor.org/biocLite.R")
biocLite("adaptest")
```
-->

Install the most recent _stable release_ from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/):

```{r gh-master-installation, eval = FALSE}
devtools::install_github("wilsoncai1992/adaptest")
```

---

<!--
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
-->
## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/wilsoncai1992/adaptest/issues).

---

## Contributions

It is our hope that `adaptest` will grow to be widely adopted as a tool for
employing data-adaptive multiple hypothesis testing procedures in
high-dimensional and complex problem settings. To that end, contributions are
very welcome, though we ask that interested contributors consult our
[`contribution
guidelines`](https://github.com/wilsoncai1992/adaptest/blob/master/CONTRIBUTING.md)
prior to submitting a pull request.

---

## Citation

After using the `adaptest` R package, please cite it:

      @article{cai2017adaptest,
        doi = {},
        url = {},
        year  = {2017},
        month = {},
        publisher = {The Open Journal},
        volume = {submitted},
        number = {},
        author = {Cai, Weixin and Hubbard, Alan E and Hejazi, Nima S},
        title = {adaptest: Data-Adaptive Statistics for High-Dimensional Testing
          in R},
        journal = {The Journal of Open Source Software}
      }

---

## License

The software contents of this repository are distributed under the GPL-2
license. See file `LICENSE` for details.

---

## References

