---
output: rmarkdown::github_document
bibliography: "README-refs.bib"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`adaptest`

[![Travis-CI Build Status](https://travis-ci.org/wilsoncai1992/adaptest.svg?branch=master)](https://travis-ci.org/wilsoncai1992/adaptest?branch=master)
[![AppVeyor Build  Status](https://ci.appveyor.com/api/projects/status/github/wilsoncai1992/adaptest?branch=master&svg=true)](https://ci.appveyor.com/project/wilsoncai1992/adaptest/)
[![Coverage Status](https://img.shields.io/codecov/c/github/wilsoncai1992/adaptest/master.svg)](https://codecov.io/github/wilsoncai1992/adaptest?branch=master)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/adaptest.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/adaptest)
[![Bioc Time](http://bioconductor.org/shields/years-in-bioc/adaptest.svg)](https://bioconductor.org/packages/release/bioc/html/adaptest.html)
[![Bioc Downloads](http://bioconductor.org/shields/downloads/adaptest.svg)](https://bioconductor.org/packages/release/bioc/html/adaptest.html)
[![GPL-2 License](http://img.shields.io/:license-gpl2-blue.svg)](http://www.gnu.org/licenses/gpl-2.0.html)
[![JOSS status](http://joss.theoj.org/papers/7618d7d14ac77f6f502df3f9eac5917d/status.svg)](http://joss.theoj.org/papers/7618d7d14ac77f6f502df3f9eac5917d)

> Data-adaptive statistics for multiple testing in high-dimensional biology

__Authors:__ [Wilson Cai](https://stat.berkeley.edu/~wcai) and [Nima
Hejazi](https://nimahejazi.org)

---

## What's `adaptest`?

The `adaptest` R package is a tool for performing multiple testing on effect
sizes in high-dimensional settings, using the approach of data-adaptive
statistical target parameters and inference. For technical details on the
data-adaptive multiple testing procedure, consult @cai2018data. For an
introduction to statistical inference procedures using data-adaptive target
parameters, the interested reader is directed to @hubbard2016statistical.

---

## Installation

For standard use, install from
[Bioconductor](https://bioconductor.org/packages/adaptest) using
[`BiocManager`](https://CRAN.R-project.org/package=BiocManager):
```{r bioc-installation, eval = FALSE}
if (!("BiocManager" %in% installed.packages())) {
  install.packages("BiocManager")
}
BiocManager::install("adaptest")
```

To contribute, install the _development version_ (i.e., branch `master`__) from
GitHub via [`devtools`](https://www.rstudio.com/products/rpackages/devtools/):

```{r gh-master-installation, eval = FALSE}
devtools::install_github("wilsoncai1992/adaptest")
```

Current and prior [Bioconductor](https://bioconductor.org) releases are
available under branches with numbers prefixed by "RELEASE_". For example, to
install the version of this package available via Bioconductor 3.7, use

```{r gh-develop-installation, eval = FALSE}
devtools::install_github("wilsoncai1992/adaptest", ref = "RELEASE_3_7")
```

**_Note_: As the first stable release of this package was through Bioconductor
v3.7, the minimum version of [R](https://www.r-project.org/) required to install
`adaptest` is 3.5.0 ("Joy in Playing").**

---

## Example

For details on how to best use the `adaptest` R package, please consult the most
recent [package
vignette](https://bioconductor.org/packages/release/bioc/vignettes/adaptest/inst/doc/differentialExpression.html)
available through the [Bioconductor
project](https://bioconductor.org/packages/adaptest).

---

## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/wilsoncai1992/adaptest/issues).

---

## Contributions

Contributions are very welcome. Interested contributors should consult our
[contribution
guidelines](https://github.com/wilsoncai1992/adaptest/blob/master/CONTRIBUTING.md)
prior to submitting a pull request.

---

## Citation

After using the `adaptest` R package, please cite the following

      @article{cai2018adaptest,
        doi = {},
        url = {},
        year  = {2018+},
        month = {},
        publisher = {The Open Journal},
        volume = {submitted},
        number = {},
        author = {Cai, Weixin and Hubbard, Alan E and Hejazi, Nima S},
        title = {{adaptest}: Data-Adaptive Statistics for High-Dimensional
          Testing in {R}},
        journal = {The Journal of Open Source Software}
      }

      @article{cai2018adaptive,
        doi = {},
        url = {https://arxiv.org/abs/1704.07008},
        year  = {2018+},
        month = {},
        publisher = {},
        volume = {},
        number = {},
        author = {Cai, Weixin and Hejazi, Nima S and Hubbard, Alan E},
        title = {Data-adaptive statistics for multiple hypothesis testing in
          high-dimensional settings},
        journal = {}
      }

---

## Funding

The development of this software was supported in part through grants from the
National Institutes of Health: [P42 ES004705-29](https://projectreporter.nih.gov/project_info_details.cfm?aid=9260357&map=y)
and [T32 LM012417-02](https://projectreporter.nih.gov/project_info_description.cfm?aid=9248418&icde=37849831&ddparam=&ddvalue=&ddsub=&cr=1&csb=default&cs=ASC&pball=).

---

## License

&copy; 2017-2018 [Wilson Cai](https://statistics.berkeley.edu/~wcai)

The software contents of this repository are distributed under the GPL-2
license. See file `LICENSE` for details.

---

## References

