---
title: "Data-mining biomarkers and perform testing"
author: "[Wilson Cai](www.stat.berkeley.edu/~wcai/), Nima Hejazi, & Alan Hubbard"
date: "`r Sys.Date()`"
output:
  # BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Data-mining biomarkers and perform testing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

The `adaptest` R package can be used to perform data-mining and high-dimensional
statistical tests that is common in differential expression studies. The package
utilizes a two stage procedure:
1. data-mining stage: reduce the dimension of biomarkers based on the
   associations of biomarkers with an exposure variable.
2. multiple testing stage: adjust for multiple testing to control false
   positives.
In this vignette, we illustrate how to use `adaptest` to perform such analysis,
using a data set containing microarray expression measures.

---

## Data-mining stage

First, we load the `adaptest` package and the (included) `simpleArray` data set:

```{r setup_data}
set.seed(1234)
library(adaptest)
data(simpleArray)
"%ni%" = Negate("%in%")
```

In order to perform Targeted Minimum Loss-Based Estimation, we need three
separate data structures: (1) _W_, baseline covariates that could potentially
confound the association of biomarkers with the exposure of interest; (2) _A_,
the point exposure of interest; and (3) _Y_, the biomarkers of interest. All
values in _A_ ought to be binarized, in order to avoid practical violations of
the assumption of positivity. To invoke the data-adaptive testing function
(`adaptest`), we also need to specify the number of top biomarkers `n_top` to
the data-mining algorithm, and the number of folds `n_fold` for cross-
validation. The smaller `n_top` is, the more selective data-mining algorithm we
have. The larger `n_fold` is, more folds are carried our in cross validaiton.

The TMLE-based biomarker discovery process can be invoked using the `adaptest`
function. The procedure is quite resource-intensive because it evaluates the
association of each individual potential biomarker (of which there are 1e3 in
the included data set) with an exposure of interest, while accounting for
potential confounding based on all other covariates included in the design
matrix. We demonstrate the necessary syntax for calling `adaptest` below:

```{r adaptest_eval, eval=TRUE}
adaptestout <- adaptest(Y = Y,
                       A = A,
                       W = NULL,
                       n_top = 10,
                       n_fold = 3,
                       parameter_wrapper = adaptest::rank_DE)
```

```{r load_adaptest_result, eval=FALSE}
data(adaptestout)
```

The output of `adaptest` is an object of class `adaptest`, containing the
following objects:
(1) top_index: (integer vector) - indices for the data-mining selected
biomarkers
(2) top_colname: (character vector) - names for the data-mining selected
biomarkers
(3) top_colname_significant_q: (character vector) - names for the data-mining
selected biomarkers, which are significant after multiple testing stage
(4) DE: (numeric vector) - differential expression effect sizes for the
biomarkers in \code{top_colname}
(5) p_value: (numeric vector) - p-values for the biomarkers in
\code{top_colname}
(6) q_value: (numeric vector) - q-values for the biomarkers in
\code{top_colname}
(7) significant_q: (integer vector) - indices of \code{top_colname} which is
significant after multiple testing stage.
(8) mean_rank_top: (numeric vector) - average ranking across cross-validation
folds for the biomarkers in \code{top_colname}
(9) folds: (origami::folds class) - cross validation object

After invoking `adaptest`, the resultant `adaptest` object will have the slots
described above completely filled in. The statistical results of this procedure
can be extracted using `summary` method.

---

## Interpret + Visualize the Results

This package provides several interpretation methods that can be used to tabular
and visualize the results of the data-adaptive tests.

The `get_composition` method for a `adaptest` object will produce a table of
composition of each data-adaptive parameters that is significant after multiple
testing stage:

```{r get_comp_small}
get_composition(object = adaptestout, type = 'small')
```

Setting the argument `type = "big"` will instead produce a table of composition
of each data-adaptive parameters before multiple testing stage, so that there
are more columns

```{r get_comp_big}
get_composition(object = adaptestout, type = 'big')
```

The `plot` method for a `adaptest` object will produce two plots that help user
interpret the results. The first plot is a plot of sorted average CV-rank for
all the biomarkers in the original dataset (`Y`). The second plot is a plot of
sorted q-values with labels corresponding to the indices of the data-adaptive
parameter (as returned in `get_composition`)

```{r plot}
plot(adaptestout)
```

---

## Session Information

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

